\begin{thebibliography}{9}
\bibitem{todo} {\color{red} hacer un parser para que quede para usar bibtex.
ver http://www.bibtex.org/}

\bibitem{adams}
Adams, R. A. (1975): \emph{Sobolev Spaces.} New York: Academic Press.

\bibitem{apelNicaise}
Apel-Nicaise etc weighted regularity 

\bibitem{duppontScott}
Duppont, T., Scott, R. (1980): \emph{Polynomial approximation of functions in Sobolev spaces},
Math. Comp., \textbf{34}, 441--463.

\bibitem{ricardoMixed}
Dur\'an, R. (a\~no ?) \emph{Galerkin Approximations and Finite Element Methods.}

\bibitem{gh99}
\emph{
@article {MR1744532,
    AUTHOR = {Gradinaru, V. and Hiptmair, R.},
     TITLE = {Whitney elements on pyramids},
   JOURNAL = {Electron. Trans. Numer. Anal.},
  FJOURNAL = {Electronic Transactions on Numerical Analysis},
    VOLUME = {8},
      YEAR = {1999},
     PAGES = {154--168},
      ISSN = {1068-9613},
   MRCLASS = {65N30 (65D15 78M10)},
  MRNUMBER = {1744532},
MRREVIEWER = {Do Young Kwak},
}}


\bibitem{nedelec1}
N\'ed\'elec, J. C. (1980): \emph{Mixed Finite Elements in $\mathbb{R}^3$}, Numer. Math. \textbf{35},
315--341.

\bibitem{nedelec2}
N\'ed\'elec, J. C. (1986): \emph{A New Family of Mixed Finite Elements in $\mathbb{R}^3$}, Numer. Math. 
\textbf{50}, 57--81.

\bibitem{ariel}
Lombardi, A. L. (2011): \emph{Interpolation error estimates for edge elements on anisotropic meshes}, 
IMA Journal of Numer. An., 1--30.

\bibitem{nicaise}
Nicaise, S. (2001): \emph{Edge elements on anisotropic meshes and approximation of the Maxwell equations},
SIAM J. Numer. Anal. \textbf{39}, 784--816.

\bibitem{buffacostabeldauge}
Buffa, A., Costabel, M., Dauge, M. (2005): \emph{Algebraic convergence for anisotro\-pic edge elements
in polyhedral domains}, Numer. Math. \textbf{101}, 29--65.

\bibitem{monk}
Monk, P. (2003): \emph{Finite Element Methods for Maxwell's Equations}, Oxford.
\end{thebibliography}